The population of long-period transiting exoplanets \vspace{-3\baselineskip}

### 2016-07-19 document/ms.tex
added isochrones reference

To determine to what extent the catalog of detections presented in this work
may contain such false positives, we simulate populations of detected signals
to predict how many we should expect.  To accomplish this, we use the Python
package
\exosyspop\footnote{\url{https://github.com/timothydmorton/exosyspop}; in this
work we use commit \textsf{e4f54288}}, which
we developed for this purpose.

>>>>

To determine to what extent the catalog of detections presented in this work
may contain such false positives, we simulate populations of detected signals
to predict how many we should expect.  To accomplish this, we use the Python
package
\exosyspop\footnote{\url{https://github.com/timothydmorton/exosyspop}; in this
work we use commit \textsf{e4f54288}}, which
we developed for this purpose and utilizes the \project{isochrones} 
package \citep{Morton:2015} for simulations of stellar populations.
